I would like to thank the Allen Institute for Artificial Intelligence for funding a large portion of the work contained here.  Additionally, this work was partially funded by the Defense Advanced Research Projects Agency (DARPA) Big Mechanism program under ARO contract W911NF-14-1-0395.

There are many many hands that have helped me along the way, and many pairs of shoulders I have stood on to get to where I am.  

Thank you to the professors who encouraged me to think I could do this, and who equipped me with the knowledge and skills to actually succeed!  Thank you to my co-advisors for their assistance all along the way.  Mihai, you invested much into my education and encouraged me to pursue my own ideas, while also allowing me to pursue some of yours. Working in your lab changed the course of my education, and subsequently my future -- thank you!  Peter, thanks for all the time you spent in the lab teaching me to tie my proverbial shoes, the papers are what they are because of you!  

I also want to thank my parents for instilling in me the understanding that an education is priceless and encouraging me from the beginning. Emily, you set a great example, and I am delighted I got to follow in your footsteps.  Nora, Isaac, and River -- you have all been a part of this journey (River may as well be a co-author!) and I wouldn't have wanted it any other way!  Dave -- this absolutely would not have been remotely possible without you, and we both know that.  I love you, and am beyond grateful for \textit{everything} you have done for me and given up so I could do this -- thank you so much! 
